Toward Intelligent Refactoring Recommendations

### 2016-08-24 Manuscript.tex
Dr. L

\input{tex/refactor}

@@

\input{tex/jur_char}

@@

\subsubsection{ Shatnawi}
Shatnawi~\cite{Shatnawi10}'s preferred alternative to $\mu+\sigma$
is to use the VARL method (Value of Acceptable Risk Level) proposed by Bender~\cite{bender99} in his epidemiology studies.  This approach uses two
thresholds which, following Shatnawi's guidance, we set to
$p_0=p_1=0.05$.\footnote{There is no p0 in the equation.}

VARL encodes the defect count
for each class as 0 (no defects known in class) or 1 (defects known in class).
Univariate binary logistic regression is applied to learn three coefficients:  
 $\alpha$ is the intercept constant;
    $\beta$ is the coefficient for maximizing log-likelihood;
  and $p_0$\footnote{There is no p0 in the equation.}  
    measures   how well this   model predicts for   defects.
Any code metric with $p_0>0.05$ is  ignored as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
an equation proposed by Bender:
\begin{equation}
 \mathit{bad\; smell\; if\;} M_c > \frac{1}{\beta }\left( {\log \left( {\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right) 
\end{equation}

@@

\subsubsection{Discussion of Outlier Methods}\label{sect:disc}
The advantage of the outlier-based
approaches is that they are simple to implement, but the approaches have   two  major disadvantages. 
First, they are {\em verbose}. A threshold can be calculated for every metric -- so, which one should the developers focus on changing? Without a means for prioritizing the  thresholds and metrics against one another, developers may have numerous or conflicting recommendations on what to improve. Second, the outlier approaches suffers from
the {\em disjunction fallacy}\footnote{It was conjunctive fallacy in the introduction -- which is right?}  discussed in the introduction.
That is, while
 they propose thresholds for many code metrics
individually, they make no comment on what minimal
metrics need to be changed at the same time (or whether or not those
changes lead to minimization or maximization of static code measures).

@@

Cluster deltas are a general method
for learning {\em conjunctions} of changes
that need to be applied at the same time. 
This approach works as follows:
\begin{itemize}
    \item Cluster the data. 
    \item Find
neighboring clusters $C_+,C_-$ where $C_+$ has more examples of defective
modules than $C_-$;
\item Compute the  delta   in code metrics between the clusters using \mbox{$\Delta = C_+ - C_-$}\footnote{Isn't this backward? Doesn't $C_- - C_+$ give you the changes to be made to $C_+$, e.g. $C_+$ = 1000LOC, $C_-$ = 100 LOC, $C_- - C_+$ = -900 LOC which is the transformation you want to apply to $C_+$}, i.e.
{\em towards} the cluster with lower defects;
\item $\Delta$ are changes needed in defective modules of $C_+$ to
      make them more like the less-defective modules of $C_-$
\end{itemize}
Note that $\Delta$ is a conjunction of  recommendations.
Since it is computed
from neighboring clusters, the examples contain similar distributions and $\Delta$ respects the naturally occurring constraints in the data. For example,
given a bad smell pertaining to large methods,   $\Delta$   will not  suggest lowering lines of code
without also increasing a coupling measure. 
Cluster deltas are used in CD~\cite{me12c} and XTREE.

@@

 XTREE uses an iterative dichotomizer that
first converts the values for each code
metric into a small number of ranges.
Consider a code metric is split into $r$ ranges and each range is of
  size
    $n_r$\footnote{How do you select $r$ and/or $n_r$?} is
  associated with a set of defect counts $x$ with standard deviation
  $\sigma_r$.
  The best split for that range is
  the one that minimizes the expected value of the
  defect variance, after the split; i.e.
  $\sum_r\frac{n_r}{n}\sigma_x$ (where $n=\sum_r n_r$).
  This discretizer then recurses on each part of the split
  to find other splits.

  When discretization finishes, each code metric $M$ has a 
  final expected value $M_v$ for the defect standard deviation 
  across all the discretized ranges of that metric.
  Iterative dichomization sorts the metrics by $M_v$
  to find the best ``splitter'' for the data
  (the code metric with smallest $M_v$). The data
  is then split on the ranges of the splitter and
  iterative dichotimization recurses on each range\footnote{I get lost here. You found the ranges to split from the smallest $M_v$ and you split the data on that. But what is the ``iterative dichotimization that recurses on each range'' at this point?}  In this way,
  each split is the root of a sub-tree.

  While not usually labelled as such, iterative dichomization can
  be viewed as a clustering algorithm that groups together code modules
  with similar defect counts and some shared ranges of code metrics.
  For our purposes, we score each cluster found in this way according
  to the percent of classes with known defects. For example,
  the last line of \fig{xtree_samp} shows a tree lead with 75\%
  defective modules.

@@

Using the training data,  XTREE uses  
iterative dichomization to
  divide  $N$ code modules  into  clusters of
size $\sqrt{N}$.

Next, for each test code module, 
	  find $C_+$ as follows take each test , run it down to a leaf in the decision tree.  
After that,	  find $C_-$ as follows:
		\begin{itemize}
		\item Starting at the  $C_+$ leaf, ascend   $lvl\in \{0,1,2...\}$ tree levels;
		\item Identify {\em sibling} leaves; i.e. leaf clusters that can be reached from level $lvl$ that are not same as {\em current }
		\item Find the {\em better} siblings; i.e. those 50\% (or less)
		fewer defects than $C_+$.\footnote{This example is for number of defects. What is your criteria for defect-proneness classification as in the Figure?}\footnote{Does XTREE stop as soon as it finds a better sibling? If it finds better siblings at level X, how do you know there are not BETTER better siblings at level X+1? It SEEMS like your dichotimization is optimized on the best performing classifier and thus you find recommendations that will result in a change, but are not optimized to find the BEST END RESULT (e.g., maximum reduction in \# of defects, maximum reduction in \% likelihood of defect proneness.}
		   If none found, then repeat for $lvl += 1$. Also,
		    return nil  if the new $lvl$ is above the root. 
		\item  Set $C_-$ to the  {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em current}
		\ei
	 Now find $\Delta = C_+ - C_-$  by reflecting
	 on the set difference between  conditions in the decision tree branch to $C_-$ and $C_+$. To find that delta,
	 for discrete attributes, the delta is the value from {\em desired};
	    for numerics  expressed as ranges, the delta is a random number selected from the low and high boundaries of the that range.\footnote{This could lead to conflicting recommendations in different runs of XTREE, right? Consider Figure 3. Suppose $C_+$ has cbo=(27.00,157.00):1.00. XTREE ascends one level and descends to the leaves of next subtree. XTREE suppose that $C_-$ is a leaft where cbo=(1.00,50:00):0.15 (instead of cam as in Figure 3). By selecting something random in the range, you could recommend either an increase or a decrease to CBO. I would think that this is an instance where XTREE should say 'I don't know what to do with CBO, but you should improve LCOM.' Alternately, if you took the median value (instead of random) and coompared, you could at least recommend a direction, i.e., ``the best benefits come from REDUCING lcom while maintaining a LOWER cbo''}

\input{tex/prediction_stats.tex}      
\section{Evaluation}
The previous section proposed numerous methods for detecting bad smells that need
to be resolved. This section offers an experiment of the following form:
\bi
\item Using each method as a {\em primary change oracle} to recommend how code should be changed.
\item Apply those changes. 
\item Run a {\em secondary verification oracle} to assess the defect-proness of the changed code.
\item Sort the change oracles on how well they reduce defects (as judged by the verification oracle).
\ei
Using this experiment, we can address the research questions dicsussed in the introduction.

@@

\subsection{Experiment}
Describe what you actually did, including: 
\bi
\item what metrics you used to identify refactorings using the 4 methods. Also, what is your data here? Is it the rows and columns of CK/OO metrics for each file?
\item how you applied the recommended changes from the 4 methods to the data 
\item how you chose to handle the ``conjuctive fallacy' of non-CD, non-XTREE methods
\item What are you considering correct, i.e., if the change to the code metrics yielded a non-defective (i.e., \# defects = 0) file, then the refactoring is good. 
\item how you aggregated the results from your 40 runs for each method
\ei

\subsection{Statistics}\footnote{You need a section before this called "Experiment"}.

@@

\input{tex/results_jur.tex}

@@

\input{tex/rq2.tex}
\section{Results}

@@

\input{tex/all_changes.tex}

@@

To explore this point further, we conducted the following ``what-if'' study\footnote{What is the advantage of this ``what-if'' approach over just looking at the recommendations from the 40 runs in your experiments? Why not both?}. Once XTREE builds its trees with its leaf clusters then:
\be
\item For all clusters $C_0$, $C_1$ where the percent of defects in $C_0$ is greater than $C_1$...
\item For all attribute measures that are have a statistically significantly different distribution  between $C_0$ and $C_1$...
\item Report the direction of the change.
\ee
Note that the changes found in this way are somewhat more general than the above results
since they were  limited
to comments on the test set given to the program. The above three points comments on the direction of {\em all possible changes}
that XTREE could ever report

@@

% \input{tex/results_models.tex}

>>>>

	\input{refactor}

@@

	\input{jur_char}

@@

	\subsubsection{ Shatnawi}
	Shatnawi~\cite{Shatnawi10}'s preferred alternative to $\mu+\sigma$
	is to use the VARL method (Value of Acceptable Risk Level) proposed by Bender~\cite{bender99} in his epidemiology studies.  This approach uses two
	constants to compute the thresholds which, following Shatnawi's guidance, we set to
	$p_0=p_1=0.05$.

	VARL encodes the defect count
	for each class as 0 (no defects known in class) or 1 (defects known in class).
	Univariate binary logistic regression is applied to learn three coefficients:  
	$\alpha$ is the intercept constant;
	$\beta$ is the coefficient for maximizing log-likelihood;
	and $p_0$ 
	measures   how well this  model predicts for  defects. A univariate logistic regression was conducted comparing metrics to defect counts. Any code metric with $p>0.05$ is ignored as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
	an equation proposed by Bender:
	$$ \mathit{bad\; smell\; if\;} M_c > VARL$$
	\begin{equation}
		VARL = p^{-1}(p_0) =  \frac{1}{\beta }\left( {\log \left( {\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right) 
	\end{equation}

@@

	\subsubsection{Discussion of Outlier Methods}\label{sect:disc}
	The advantage of the outlier-based
	approaches is that they are simple to implement, but the approaches have   two  major disadvantages. 
	First, they are {\em verbose}. A threshold can be calculated for every metric -- so, which one should the developers focus on changing? Without a means for prioritizing the  thresholds and metrics against one another, developers may have numerous or conflicting recommendations on what to improve. Second, the outlier approaches suffers from {\em conjunctive fallacy}  discussed in the introduction. That is, while	they propose thresholds for many code metrics
	individually, they make no comment on what minimal metrics need to be changed at the same time (or whether or not those changes lead to minimization or maximization of static code measures).

@@

	Cluster deltas are a general method
	for learning {\em conjunctions} of changes
	that need to be applied at the same time. 
	This approach works as follows:
	\begin{itemize}
		\item Cluster the data. 
		\item Find
		neighboring clusters $C_+,C_-$ where $C_+$ has more examples of defective
		modules than $C_-$;
		\item Compute the  delta   in code metrics between the clusters using \mbox{$\Delta = C_- - C_+ = \left\{\delta|\delta\in C_-, \delta \notin C_+\right\}$}, i.e.
		{\em towards} the cluster with lower defects;
		\item The set $\Delta$ are changes needed in defective modules of $C_+$ to
		make them more like the less-defective modules of $C_-$
	\end{itemize}
	Note that $\Delta$ is a conjunction of  recommendations.
	Since it is computed
	from neighboring clusters, the examples contain similar distributions and $\Delta$ respects the naturally occurring constraints in the data. For example,
	given a bad smell pertaining to large methods,   $\Delta$   will not  suggest lowering lines of code
	without also increasing a coupling measure. 
	Cluster deltas are used in CD~\cite{me12c} and XTREE.

@@

	XTREE uses a multi-interval discretizer based on an iterative dichotomization scheme, first proposed by Fayyad and Irani~\cite{fi}. This method converts the values for each code metric into a small number of nominal ranges. It works as follows:
	\begin{itemize}
		\item A code metric is split into $r$ ($r=2$) ranges, each range is of
		size $n_r$ and is associated with a set of defect counts $x$ with standard deviation
		$\sigma_r$. 
		\item The best split for that range is the one that minimizes the expected value of the
		defect variance, after the split; i.e. $\sum_r\frac{n_r}{n}\sigma_x$ (where $n=\sum_r n_r$). 
		\item This discretizer then recurses on each part of the split to find other splits in a recursive fashion. As suggested by Fayyad and Irani, minimum descriptor length (MDL) is used as a termination criterion for the recursive partitioning.
	\end{itemize}

	When discretization finishes, each code metric $M$ has a 
	final expected value $M_v$ for the defect standard deviation 
	across all the discretized ranges of that metric.
	Iterative dichomization sorts the metrics by $M_v$
	to find the code metric that best splits the data i.e., the code metric with smallest $M_v$.

	A decision tree is then constructed on the discretized metrics. The metric that generated the best split forms the root of the tree with its discrete ranges acting as the nodes.

	When all the metrics are arranged this way, the process is very similar to a hierarchical clustering algorithm that groups together code modules with similar defect counts and some shared ranges of code metrics.
	For our purposes, we score each cluster found in this way according
	to the percent of classes with known defects. For example, the last line of \fig{xtree_samp} shows a tree leaf with 75\%
	defective modules.

@@

	Using the training data construct a decision tree as suggested above.

%	uses  
%	iterative dichomization to
%	divide  $N$ code modules  into  clusters of
%	size $\sqrt{N}$.

	Next, for each test code module, 
	find $C_+$ as follows: take each test, run it down the decision tree to find a leaf in the decision tree that mostly matches the test case.  
	After that,	find $C_-$ as follows:
	\begin{itemize}
		\item Starting at the  $C_+$ leaf, ascend $lvl\in \{0,1,2...\}$ tree levels;
		\item Identify {\em sibling} leaves; i.e. leaf clusters that can be reached from level $lvl$ that are not same as {\em current $C_+$};
		\item Find the {\em better} siblings; i.e. those 50\% (or less)
		fewer defects than $C_+$. If none found, then repeat for $lvl += 1$. Also, return \texttt{nil} if the new $lvl$ is above the root. 
		\item  Set $C_-$ to the  {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em current}
		\ei
		Now find $\Delta = C_- - C_+$  by reflecting
		on the set difference between  conditions in the decision tree branching from $C_+$ to $C_-$. To find that delta,
		for discrete attributes, delta is the value of the {\em desired}; for numerics  expressed as ranges, the delta could be any value that lies between $\left[ LOW, HIGH\right]$ in that range (random number selected from the low and high boundaries of the that range.)

		\input{prediction_stats.tex}      
		\section{Evaluation}
		The previous section proposed numerous methods for detecting bad smells that need
		to be resolved. This section offers an experiment of the following form:
		\bi
		\item Using each method as a {\em primary change oracle} to recommend how code should be changed.
		\item Apply those changes. 
		\item Run a {\em secondary verification oracle} to assess the defect-proness of the changed code.
		\item Sort the change oracles on how well they reduce defects (as judged by the verification oracle).
		\ei
		Using this experiment, we can address the research questions dicsussed in the introduction.

@@

%		\subsection{Experiment}
%		Describe what you actually did, including: 
%		\bi
%		\item what metrics you used to identify refactorings using the 4 methods. Also, what is your data here? Is it the rows and columns of CK/OO metrics for each file?
%		\item how you applied the recommended changes from the 4 methods to the data 
%		\item how you chose to handle the ``conjuctive fallacy' of non-CD, non-XTREE methods
%		\item What are you considering correct, i.e., if the change to the code metrics yielded a non-defective (i.e., \# defects = 0) file, then the refactoring is good. 
%		\item how you aggregated the results from your 40 runs for each method
%		\ei
%

		\subsection{Statistics}

@@

		\input{results_jur.tex}

@@

		\input{rq2.tex}
		\section{Results}

@@

		\input{all_changes.tex}

@@

		To explore this point further, we conducted the following ``what-if'' study. Once XTREE builds its trees with its leaf clusters then:
		\be
		\item For all clusters $C_0$, $C_1$ where the percent of defects in $C_0$ is greater than $C_1$...
		\item For all attribute measures that are have a statistically significantly different distribution  between $C_0$ and $C_1$...
		\item Report the direction of the change.
		\ee
		Note that the changes found in this way are somewhat more general than the above results
		since they were  limited
		to comments on the test set given to the program. The above three points comments on the direction of {\em all possible changes}
		that XTREE could ever report

@@

		% \input{results_models.tex}
